\beginnumbering
\pstart
\eledsection*{A first heading}

\pend
\pstart
The following paragraf with \edtext{critical text in aparatus A}{\lemma{critical text in aparatus A\rbracket}\Aendnote{The footnote not too short}} and end. And some more text to detect hanging indent? Should be nice to fix in template. 

\pend
\pstart
\eledsection*{A second heading}

\pend
\pstart
In this case there is no extra space after the heading and repeat above: The following paragraf with \edtext{the lemma in \emph{bold} A}{\lemma{the lemma in \emph{bold} A\rbracket}\Aendnote{A longer endnote to use in the end of the document just to check the hanging indent. I can \textbf{boogie} and yes.}} and end. And some more text to detect hanging indent? Should be nice to fix in template.\newline
Using the hard line break above. 

\pend
\pstart
Williamsburg \edtext{asymmetrical pork belly messenger bag. Kitsch photo booth Godard}{\lemma{asymmetrical\ldots{}Godard\rbracket}\Aendnote{The shorter and a new paragraf lemma}} forage, scenester twee hoodie listicle selvage. Echo Park small batch pork belly master cleanse. Bicycle rights freegan mumblecore migas, mixtape Williamsburg shabby chic crucifix salvia asymmetrical quinoa Wes Anderson PitchforkDIY. 3 wolf moon freegan YOLO leggings fixie 8-bit. Authentic kitsch keffiyeh, trust fund Williamsburg beard freegan gastropub cardigan flexitarian tattooed vinyl meggings. Salvia health goth drinking vinegar, Odd Future polaroid bitters whatever 90's meditation chambray tote bag.

\pend
\pstart
Semiotics Blue Bottle irony, keffiyeh street art typewriter PBR-B deep v Odd Future XOXO hella twee. Lomo keytar mixtape Odd Future Pitchfork plaid. Kale chips mustache ennui, twee Neutra freegan photo booth squid Tumblr Truffaut meh stumptown. Pickled pour-over next level, listicle stumptown art party narwhal farm-to-table roof party selfies yr ennui cred. Organic Carles tattooed forage ugh shabby chic. Butcher Austin try-hard, sustainable selfies gentrify Williamsburg Godard viral +1 flexitarian polaroid Banksy ennui. Readymade cold-pressed keytar salvia, viral normcore banh mi skateboard.

\pend
\endnumbering

\beginnumbering
\pstart
\eledsection*{Cap 2}

\pend
\pstart
The following paragraf with \edtext{critical text in aparatus B}{\lemma{critical text in aparatus B\rbracket}\Bendnote{The footnote not too short}} and end. And some more text to detect hanging indent? Should be nice to fix in template. 

\pend
\pstart
\eledsection*{A Third  in chapter two}

\pend
\pstart
In this case there is no extra space after the heading and repeat above: The following paragraf with \edtext{the lemma in \emph{bold} B}{\lemma{the lemma in \emph{bold} B\rbracket}\Bendnote{A longer endnote to use in the end of the document just to check the hanging indent. I can \textbf{boogie} and yes.}} and end. And some more text to detect hanging indent? Should be nice to fix in template.\newline
Using the hard line break above. 

\pend
\pstart
Semiotics Blue Bottle irony, keffiyeh street art typewriter PBR-B deep v Odd Future XOXO hella twee. Lomo keytar mixtape Odd Future Pitchfork plaid. Kale chips mustache ennui, twee Neutra freegan photo booth squid Tumblr Truffaut meh stumptown. Pickled pour-over next level, listicle stumptown art party narwhal farm-to-table roof party selfies yr ennui cred. Organic Carles tattooed forage ugh shabby chic. Butcher Austin try-hard, sustainable selfies gentrify Williamsburg Godard viral +1 flexitarian polaroid Banksy ennui. Readymade cold-pressed keytar salvia, viral normcore banh mi skateboard.

\pend
\endnumbering
